%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

%% Resume Version: 1

\documentclass[]{ahmedamrcv}

% For mathematical symbols
\usepackage{amsmath}

% Header info
\name{Ahmed Amr Abdulfattah}
\address{Linkedin: ahmedamron \linebreak Github: ahmedamron \linebreak UVa: AhmedAmrOn}
\contacts{Egypt: +21155128882 \linebreak ahmedamron@gmail.com \linebreak}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Senior Python/Data Engineer}{Opinov8/EnergyAspects (Ukraine/UK)}{April 2021 -- Now}
			\begin{itemize}
				\item Lead development of the following areas:
				\begin{itemize}
					\item Redesigning legacy infrastructures and improving data architecture.
					\item Build a centralized data warehouse and pipelines to collect and process data using dbt from numerous sources and provide daily actionable insights.
					\item Architect, implement, and maintain core internal APIs for data modeling using FastAPI, CloudBuild, Cloud Firestore, Artifact Registry, and Cloud Run Services/Jobs).
					\item Architect, implement, and maintain core public APIs for data delivery.
					\item Implement and maintain several ETL processes to relational dbs/time-series dbs.
					\item Improve data engineering best practices, including code reviews, quality monitoring, and knowledge sharing.
					\item Creating and deploying org-wide dash app templates along with Auth0 integration.
					\item Performing Environment/DAGs migration (prior/post) Cloud Composer/Airflow upgrades.
					\item Building data-related CI/CD pipelines using (Cloud Build/ Github Actions)
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Lead Data Engineer}{Akawin (US)}{May 2023 -- Sep 2023}
			\begin{itemize}
				\item Built real-time ETL data pipelines that collect data from a distributed social network following nostr protocol then integrate with GraphDB, AWS DocumentDB, ElasticSearch, and AWS ElastiCache.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Lead Data Engineer}{Concentrical (US)}{Jan 2022 -- Jun 2022}
			\begin{itemize}
				\item Lead Migration of Data Platform and Separation of ITK and Concentrical
				\item Architecting/Implementing data deletion endpoints to delete org-level data from all five internal microservices databases/systems + any AWS resources/backups.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Lead Data Engineer}{InsideTrack (US)}{Aug 2018 -- Jan 2022}
			\begin{itemize}
				\item Leading Development/Maintenance of the Data Infrastructure behind uCoach app which includes:
				\begin{itemize}
					\item ETL Pipelines responsible for ingesting data from 40+ US Universities with different frequencies, transform to consolidate, then load into uCoach Microservices.
					\item Passback Jobs: Extracts from DW (Both AWS Redshift, then later Snowflake) data sent back to clients.
					\item Workflows Orchestration Internal Manager.
					\item Internal ETL tool (https://github.com/inside-track/pemi) (Currently outsourced)
					\item Real-time syncing tools (Fivetran, Stitch, and previously Alooma)
					\item Data Warehouse Modeling, dbt jobs
					\item Setting Team OKRs.
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Staff Data/Analytics Engineer}{Rubikal}{Summer 2018 -- Now}
			\begin{itemize}
				\item Leading the Data Engineering/Analytics teams for all of client's projects.
				\item Growing the data engineering team technical and personal aspects.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Lead Data Engineer}{Endless Studios}{April 2021 -- Jul 2021}	
			\begin{itemize}
				\item Architecting/Building a customized data engineering pipeline to ETL data from different sources into Google BigQuery.
				\item Help building refreshable DW analytical models (Data Marts).
				\item Automating the whole ETL process/DW refresh process.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Senior Software Engineer}{IMAGO (Germany)}{Dec 2020 -- Feb 2021}	
			\begin{itemize}
				\item Developed a cross-platform scripts that uses FFMPEG to process videos and generate a watermarked set of videos with different resolutions.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Senior Software Engineer}{College Confidential (US)}{Dec 2020 -- Feb 2021}	
			\begin{itemize}
				\item Lead development of forums tagging project by tagging 1.5M posts with college/university/educational institutions name tags based on content.
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Senior Software Engineer}{Benchmarq (US)}{Dec 2020 -- Feb 2021}	
			\begin{itemize}
				\item Architecting data infrastructure to support timeseries forecasting.
				\item Performing ETL for sources like (GDELT (https://www.gdeltproject.org/), and internal relation databases etc..)
				\item Training models in AWS Amazon Forecast for forecasting of events.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Teaching Assistant}{AAST (CS Department)}{Feb 2017 -- Aug 2019}
			\begin{itemize}
				\item Taught on-campus courses of Computing Algorithms, OOP, and Data Visualization
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Data Engineer}{BADR}{Mar 2017 -- Jun 2017}
			\begin{itemize}
				\item Implemented a product that analyses Wuzzuf job posts for:
				\begin{itemize}
					\item Recruiters: to reveal needed skills per job title to hire for, and help recruiters write job descriptions.
					\item Job Seekers: to reveal needed skills of active jobs current market hire for
				\end{itemize}
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Incorta}{Mar 2016 -- Dec 2016}
			\begin{itemize}
				\item Implemented a d3.js visualization library that contains the following graphs (Horizontal Bar Chart, Vertical Bar Chart, Line Chart, Line Bar Chart, Stacked Bar Chart, Grouped Bar Chart, Area chart, Spider Chart, Bubble Chart, Heatmap Chart, Scatter plots, Bubble Map Chart, Geo Maps).
			\end{itemize}
		\end{cvsubsection}


		\begin{cvsubsection}{Software Engineer}{WhoKnows (US)}{Dec 2016 -- Mar 2017}
			\begin{itemize}
				\item Project Scope: Implement and Integrate six pages with 30 Charts into WhoKnows web app
				\begin{itemize}
					\item Implemented SQL queries to provide data per graph.
					\item Implemented RESTful APIs to return data needed per graph.
					\item Used Angular.js and angular-nvd3 to implement some of the charts in the frontend.
				\end{itemize}
				
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Software Engineer}{Elite HRV (US)}{Jul 2016 -- Sep 2016}
			\begin{itemize}
				\item Implemented a couple of features like adding tagging features, and adding breathing options to their cross-platform mobile app using ionic.
			\end{itemize}
		\end{cvsubsection}

	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Alexandria, EG}{Alexandria University}{2010 -- 2015}
			\begin{itemize}
				\item B.S in Computer and Systems Engineering.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Systems Programming; Computer Vision.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Side Projects}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
    			\item \textbf{Wikipedia Daily Hot Topics}. App shows top N topics visited. (Python, Hadoop, JS)
				\item \textbf{Distributed Multi-Agent Classifier}. Classify items based on collected data by agents from multiple distributed locations. (Java, JADE)
				\item \textbf{Twitter Sentiment Analysis}. App that infers sentiment of tweets. (Python, Machine Learning, JS)
				\item \textbf{XO Game with AI Using Assembly }. XO game with MinMax algorithm. (X86 Assembly)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	

	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Languages} Python, Java, JavaScript and C
				\item \textbf{Databases}  Relational DBs, NoSQL DBs, and Timeseries DBs
				\item \textbf{Cloud Services}  Google Cloud and AWS
				\item \textbf{Deployment/CI/CD}  Docker, K8s, CircleCI, Github Actions, terraform and CloudBuild
				\item \textbf{Data Related}  Hadoop, Spark, Redshift, Snowflake, Tableau
				\item \textbf{Concepts}  Microservices, Machine Learning, and Leadership
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\end{document}
